Abstractions for Multi-Sorted Substitutions

### 2023-09-20 paper/paper.tex
Update.

  \emph{Autosubst}\cite{DBLP:conf/itp/SchaferTS15}
  is a Coq framework, which derives parallel substitution definitions and
  lemmas for languages from annotated Coq syntax definitions using
  extrinsic typing, extrinsic scoping, and de Bruijn indices.
  The framework is implemented in Coq's tactic language LTAC and comes
  with a decision procedure for all assumption-free, equational
  substitution-lemmas.
  The implementation of Autosubst deals with multiple variable sorts
  by generating multiple substitutions and corresponding interaction lemmas.

>>>>

  \emph{Autosubst}\cite{DBLP:conf/itp/SchaferTS15}
  is a Coq framework, which derives parallel substitution definitions and
  lemmas for languages from annotated Coq syntax definitions using
  extrinsic typing, extrinsic scoping, and de Bruijn indices.
  The framework is implemented in Coq's tactic language Ltac and comes
  with a decision procedure for all assumption-free, equational
  substitution-lemmas.
  The implementation of Autosubst deals with multiple variable sorts
  by generating multiple substitutions and corresponding interaction lemmas.
